---
title: "Data Understanding for Mercari Price Suggestion"
author: "Markus Loide"
date: "10 detsember 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(dplyr)
library(ggplot2)
```

# Reading the data

```{r}
train_data <- fread("data/train.tsv", na.strings="")
```

```{r, echo=FALSE, eval=FALSE}
train_data
```

```{r}
colnames(train_data)
```

Amount of rows in the training dataset

```{r}
nrow(train_data)
```

```{r}
str(train_data)
```


## Name

Number of different names in the dataset 

```{r}
length(unique(train_data$name))
```

Number of missing values

```{r}
length(train_data[is.na(train_data$name), ])
```

## Item condition

Different values for condition

```{r}
length(unique(train_data$item_condition_id))
```

Missing values

```{r}
nrow(train_data[is.na(train_data$item_condition_id), ])
```

Distribution of item conditions

```{r}
ggplot(train_data, aes(x = item_condition_id)) + geom_bar()
```

The distributions for the different values of item condition are heavily skewed towards to lower numbers. As such, it might be necessary to use sampling.

## Item category

Unique values

```{r}
length(unique(train_data$category_name))
```

Missing values

```{r}
nrow(train_data[is.na(train_data$category_name), ])
```

Distribution

```{r}
ggplot(train_data, aes(x = category_name)) + geom_bar()
```

As with the last one, here some categories are represented very little. A solution for this can also be found with sampling.


## Brand name

```{r}
length(unique(train_data$brand_name))
```

```{r}
nrow(train_data[is.na(train_data$brand_name), ])
```

Average price depending whether or not brand name exists

```{r}
train_data %>%
  group_by(is.na(brand_name)) %>%
  summarise(average_price = mean(price), average_price_stdev = sd(price), max_price = max(price), min_price = min(price))
```

## Shipping info

```{r}
train_data$shipping <- as.factor(train_data$shipping)
```

```{r}
ggplot(train_data, aes(x = shipping)) + geom_bar()
```

Pretty equal - good.

## Item description

Written in free form, no use even trying to see how many are different.

## Price

```{r}
max(train_data$price)
min(train_data$price)
mean(train_data$price)
```



```{r}
ggplot(train_data, aes(x = price)) + geom_bar()
```

Also a case for sampling perhaps.